\bf A Concise Survey on Statistical Analysis in Bike Lane Research

### 2023-11-13 Manuscript/Manuscript.tex
added to results section

\begin{abstract}
This survey paper examines the evolving field of statistical analysis of bicycle lanes. Cycling has an evolving role in society, and has taken a place as a sustainable and accessible mode of transportation and exercise. In order for cycling to be accessible for the most number of people, investments into bike lanes and cycling infrastructure have to be made. Through an examination of existing studies, we explore the current trends in method to show whether bike lanes have a statistically significant effect on cycling outcomes. 
\end{abstract}
\label{sec:abstract}

@@

The correlation and regression analysis approach of statistical research on bicycle lanes is used to establish significant relationships amongst variables. In \citet{1MateoBabiano2016}, the approach using Spearman's correlation coefficient rho was used, which was suitable because the variables deviated from a normal distribution. The variables used were Public bicycle-sharing programs (PBSP) station usage frequency and length of bike-ways, which do not follow a normal distribution. The results of the Spearman correlation of station usage and infrastructure type can be seen in ~\ref{table:MB}, where shred pathways, bicycle paths, connections, and separated pathways were shown to have a significant impact on PBSP usage. 
1, 2, 7 .

>>>>

\begin{abstract}
This survey paper examines the evolving field of statistical analysis of bicycle lanes. Cycling has an important role in society, and has taken a place as a sustainable and accessible mode of transportation and exercise. In order for cycling to be accessible for the most number of people, investments into bike lanes and cycling infrastructure have to be made. Through an examination of existing studies, we explore the current trends in method to show whether bike lanes have a statistically significant effect on cycling outcomes. 
\end{abstract}
\label{sec:abstract}

@@

The correlation and regression analysis approach of statistical research on bicycle lanes is used to establish significant relationships amongst variables. In \citet{1MateoBabiano2016}, the approach using Spearman's correlation coefficient rho was used, which was suitable because the variables deviated from a normal distribution. The variables used were Public bicycle-sharing programs (PBSP) station usage frequency and length of bike-ways, which do not follow a normal distribution. The results of the Spearman correlation of station usage and infrastructure type can be seen in ~\ref{table:MB}, where shred pathways, bicycle paths, connections, and separated pathways were shown to have a significant impact on PBSP usage. \par
Other analyses used include Differences-in-Differences, Pearson's R correlation coefficient, Panel regressions, and Counterfactual based on control \cite{Karpinski2021}. These were used when the data being analyzed was usership of Boston's bike share program before and after the addition of bike lanes.
